\propertitle

### 2019-06-19 maxNt_v5.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-06-19T11:23:16+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

We first calculate the maximum-entropy distribution for the full network by
using six moments. This number already provides as much information as the
full frequency distribution of the sample, and at the same time illustrates
the use of the approach in questions of statistic sufficiency (typically
limited to two or three moments). We show the results for full-network
sizes $N=1\,000$, $N=5\,000$, $N=10\,000$\mynote{motivate?}. Thereafter we
show the results for two moments and six moments using $N=10\,000$.

\begin{figure}[!b]
\centering
\includegraphics[width=\linewidth]{scripts/paper_stensola_6mom_distributionsN_prior2.pdf}%
\\%
\includegraphics[width=\linewidth]{scripts/paper_riehle_6mom_distributionsN_prior2.pdf}%
\caption{***}
\label{fig:plots_6mom}
\end{figure}
%maxent_solutions_different_moments_prior2_6moments.nb

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-06-19T13:30:42+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

We first calculate the maximum-entropy distribution for the full network by
using six moments. This number already provides as much information as the
full frequency distribution of the sample, and at the same time illustrates
the use of the approach in questions of statistic sufficiency (typically
limited to two or three moments). Figure~\ref{fig:plots_6mom} shows the
resulting densities (distribution/activity-step, that is,
distribution${}\times N$) for full-network sizes $N=n$, $N=1\,000$,
$N=5\,000$, $N=10\,000$\mynote{motivate?}. The case $N=n$ corresponds to
applying the maximum-entropy method at the sample level.

Thereafter we show the results for two moments and six moments using
$N=10\,000$.

\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{scripts/paper_stensola_6mom_distributionsN_prior2.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{scripts/paper_riehle_6mom_distributionsN_prior2.pdf}%
\caption{***}
\label{fig:plots_6mom}
\end{figure}
%maxent_solutions_different_moments_prior2_6moments.nb
